Combined Data Cleaning and Statistical Analysis Script for Manuscript: Salmonella Environmental Persistence Informs Management Relevant to Avian and Public Health

### 2023-04-24 3. Analysis Script/StatisticalAnalysis.qmd
Analysis Edits continued...

#**Time to event**
```{r}
library(finalfit)
library(forcats)

ff_glimpse(PT_Data)

PT_Data= PT_Data %>%
  mutate(

  )
```

#**Cox regression**
```{r}
```

>>>>

#**Time to event**
```{r}
#KP needs to edit this! Not running as expected....

library(finalfit)
library(forcats)
library(survival)

as.Date(PT_Data$Date, format= "%Y-%M-%D")

PT_Data$Date<- as.numeric(PT_Data$Date)

PT_Data = PT_Data %>% 
  mutate(
    Salmonella_Positive_os = ifelse(Salmonella_Positive == 0,1,0),
      status_crr= case_when(
        `Salmonella_Positive` == 1~0,
        `Salmonella_Positive` == 1~1))

dependent_crr= "Surv(Date, status_crr)"
explanatory= c("Table", "Quadrant", "Sample_Type")

PT_Data %>% finalfit(dependent_crr, explanatory)

PT_Data %>% 
   finalfit(dependent_crr, explanatory, add_dependent_label = FALSE) %>% 
    rename("Overall survival" = label) %>% 
    rename(" " = levels) %>% 
    rename("  " = all) 
```

#**Cox regression: Picnic Table Data**
```{r}

as.Date(PT_Data$Date, format= "%Y-%M-%D")

PT_Data$Date<- as.numeric(PT_Data$Date)

coxph(Surv(Date, Salmonella_Positive) ~ Sample_Type, PT_Data)

coxph(Surv(Date, Salmonella_Positive) ~ Sample_Type, PT_Data) %>%
  tbl_regression(exp=TRUE)
```
#**Cox regression: Feeder Data**
```{r}
library(lubridate)

#Date needs to be fixed in this DS

FD_Data <- FD_Data %>%
  mutate(Collection_Date=lubridate::dmy(Collection_Date))

FD_Data$Collection_Date<- as.numeric(FD_Data$Collection_Date)

coxph(Surv(Collection_Date, Absence_0_Presence_1 ~ Sample_Type, FD_Data))

coxph(Surv(Date, Salmonella_Positive) ~ Sample_Type, PT_Data) %>%
  tbl_regression(exp=TRUE)
```
